Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-04-07 docs/ms.tex
Update ms.tex

@@

Due to the limitation of galaxy number we are not able to get an exact value for m and c.However in our result 
both the most-like and uncertainty of m are around $10^{-3}$ and for c they are around $10^{-4}$ . Due to the
relatively large uncertainty, it is only an rough estimate of bias level.

@@

We compare the mean square error of our estimator with average and
the estimator that could be constructed if the true unlensed ellipticity
distribution were known. We show how the mean square error varies
with number of galaxies, number of patches and so on.

>>>>

\begin{figure}
\end{figure}
\begin{figure}
\includegraphics[scale=0.2]{fig/test10}

\caption{The figure shows the posterior samples of reduced shear g
in all the 64 patches . The two blues lines indicate the poisition of
true(input) $g_{1}$ and $g_{2}$. The Blue '+' shows the position
of sample mean, while the red '+' shows the result of mean ellipticity
estimator.}
\end{figure}

@@

Due to the limitation of galaxy number we are not able to get an exact value for m and c.However in our result 
both the most-like and uncertainty of m are around $10^{-3}$ and for c they are around $10^{-4}$ . Due to the
relatively large uncertainty, it is only an rough estimate of bias level.
\begin{figure}
\includegraphics[scale=0.5]{fig/g1bias}

\caption{The figure shows the estimated $g_{1}$ values minus the true (input)
$g_{1}^{true}$ . The distribution range of $g_{1}^{true}$ is from
-0.1 to 0.1. Originally there are 640,000 true $g_{1}$. We bin the
plot for presentation purpose. The data point and error bars are the weighted
 average and  variance of $\delta g_{1}$ in each bin.The blue
line is the result of weighted linear fit of the original 640,000 data points
with sample standard deviation as error bar.}
\end{figure}

@@

We compare the mean square error of our estimator with average and
the estimator that could be constructed if the true unlensed ellipticity
distribution were known. We show how the mean square error varies
with number of galaxies, number of patches and so on.
\begin{figure}
\includegraphics[scale=0.5]{fig/Np_step}

\includegraphics[scale=0.5]{fig/N16NP_vary}

\caption{The upper panel shows how the mean square error of g estimates varies
with the number of patches used with 8 galaxies in each patch. The
lowwer panel shows the same thing with 16 galaxies in each patch. }
\end{figure}
